Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors That Have Mixed During Cooling

### 2019-09-01 paper/reply_to_referee.txt

> - Why were the models calculated in this paper ignited at the center,
> unlike the models in Willcox et al (2016)? Note that you invoke the
> off-center ignition as one of the causes of the differing results, but you
> do not provide a justification of the different ignition configuration.

Something else we could have better explained. The hybrid models in Willcox
et al have a very different structure with the highest temperature, where
ignition of the deflagration is expected, at a radius of about 300 km. 
The profiles are illustrated in Figures 2 and 9 of Willcox et al. Yet 
another thing we have made clear in the revised manuscript.

> - In the first paragraph of section 3, it is argued that the yield of 56Ni
> was approximated by assuming the composition upon NSE freeze-out is 56Ni
> plus equal parts 54Fe and 58Ni. However, in many models of supernova Ia
> there is a large abundance of 56Ni in the layers that do not go beyond
> QNSE. Have you corrected for this effect somehow?

[Hmmm. I think this is not right. What to say?] 
The estimate of 56Ni yield does follow from assuming the NSE mix is
composed of 56Ni plus equal parts 54Fe and 58Ni, and this approach is
how all 56Ni in the simulation is calculated. 56Ni in (outer) layers
that did not go beyond QNSE would have been synthesized by fusion 
going to the Fe-group and then mixed. As such, the estimate we use 
should be robust. We have added a sentence with citations and an
additional citation to previous work verifying this approach in a variety 
of scenaros to the paragraph.

@@

> *General*

> - Which is the role played by the hybrid progenitors in the global plot of
> supernovae type Ia? Since the lower limit of the 56Ni mass distribution
> is 0.6 solar masses, does it mean that hybrid progenitors lead to
> normal-to-bright supernovae while C+O progenitors represent the brighter
> end of this kind of supernovae? Does it imply a dominant contribution
> of double degenerate channel for the normal supernovae Ia? Most readers
> would thank a brief discussion of these and related issues.

These are the questions that we are exploring with this and related work,
and we regret not make these clear in the introductory material. We
have added text addressing exactly these issues.

@@

TO BE DONE

> - Subsections 1.1 and 1.2 are more typical of a review than a regular
> paper, and are not at all necessary to understand what follows. They
> should be shortened to one or two medium length paragraphs. By the way,
> the reference Nomoto et al (1984) does not match the description of the
> flame that precedes it.

> - Figures 3, 6, and 7 are not quite informative, and the same applies
> to the short mention of them in the text. The authors should consider
> removing them.

We appreciate the referee's point. The figures show the evolution of quantites 
like 56Ni abundance with time and are similar to some of the figures showing 
abundance evolution in Willcox et al. Because they allow the reader to both 
visualize the scatter in the yields and also the character of the burning 
(such as the DDT), we feel they are useful and would like to keep them. Also,
they are similar to figures in Willcox et al, which allows comparison
to results from another class of hybrid progenitors. We agree with the referee 
that the discussion was scant and have improved that.

### 2019-09-01 paper/ms.tex
More work on the referee's report. Getting there.

@@

The need for a model flame in simulating thermonuclear supernovae follows
from the scales of the problem. At high densities, the width of a laminar
nuclear flame is $< 1\ensuremath{\;}{\ensuremath{\mathrm{cm}}}$ while the
radius of the white dwarf $\sim 10^9\ensuremath{\;}{\ensuremath{\mathrm{cm}}}$.
Even with adaptive mesh refinement, whole-star simulations cannot
simultaneously resolve the nuclear flame, so simulations require a model to
describe the burning on unresolved scales.  The model we apply is a flame
capturing scheme and thermally-activated burning module to describe
thermonuclear burning during both the deflagration and detonation phases,
as well as routines to describe the evolution of the dynamic ash.
This description of the burning was developed during the course of research in
thermonuclear supernovae and has been presented in a series of
papers \citep[See][and references therein]{chandlery}. For completeness,
we briefly review the flame capturing scheme here.

@@

We frame the presentation of the results of the suites of simulations
principally in terms of the yield of \Ni{56}, the energy source of
the light curve of an event. \Ni{56} thus serves as a proxy
for the brightness of an explosion and comparison of the yields
is equivalent to comparing the brightness of events. The
yields were estimated from $Y_e$ and the NSE progress
variable, by assuming the composition upon NSE freeze-out is \Ni{56} plus equal
parts \Fe{54} and \Ni{58} \citep{townetal2009,Meaketal09}.
This assumption allows the fraction of IGEs in the form of \Ni{56} to be estimated from the $Y_e$ tracked by the burning model.

\begin{figure}
\includegraphics[width=\columnwidth]{figures/cum_dis_Ni56.pdf}
\caption{\label{fig:cumdist}
The cumulative distribution of the final \Ni{56} yield for explosions from
C-O (red) and hybrid C-O-Ne (blue) models.
The curve for the hybrid models is shifted
to the left, indicating that explosions from hybrid progenitors produce
less \Ni{56} than explosions from traditional C-O models with the same central density.
}
\end{figure}
The cumulative distribution of the \Ni{56} yield for explosions from
C-O and hybrid C-O-Ne models is presented in Figure \ref{fig:cumdist}.
Average and standard deviations of the sample of yields and kinetic energies are given in Table~\ref{tab:ave_yields}.
The figure shows that the hybrid models consistently have a higher
cumulative fraction at a given mass of \Ni{56}, which indicates
that the yields of \Ni{56} are consistently lower in explosions
from hybrid progenitors of the same central density.
This contrast is in a similar direction but not as large as the difference between C-O and C-O-Ne progenitors seen in \citep{willcoxetal2016}.
{\color{red} CHECK FORMAT OF WILLCOX CITATION}

@@

The expected final production of \Ni{56}, after NSE freeze-out, as a function of simulation time
for 10 simulations of explosions from each progenitor is shown in Figure \ref{fig:nithybrid}.
On average, the C-O model reaches the DDT phase sooner then the
hybrid model.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/RatioNi56IGE_v_time_plot.pdf}
\caption{\label{fig:compare_ratio}
Expected ratio of \Ni{56} to total IGE production by mass vs.\ time showing the evolution
for both suites of simulations. Results from C-O-Ne progenitors are in blue and C-O progenitors in red.
%SAME AS DON'S FIGURE 19
}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{figures/MBTI_v_time_plot.pdf}
\caption{\label{fig:compare_burned}
Plot of estimated mass burned to IGEs vs.\ time showing the evolution
for both suites of simulations for realizations 25-30. Results from C-O-Ne progenitors are
in blue and C-O progenitors red.
%SAME AS DON'S FIGURE 20
}
\end{figure}

The fraction, by mass, of IGE material expected to be in the form of \Ni{56} after freeze-out is shown in Figure \ref{fig:compare_ratio} as it evolves in time.
Also shown in Figure~\ref{fig:compare_burned} is the concurrent evolution of mass burned to IGE for both suites.
The total IGE has a mostly similar evolution, but the ratio demonstrates important differences between C-O and C-O-Ne cases.

>>>>

{\color{blue} 
Discerning the role played by hybrid progenitors in the global gamut of
thermonuclear is the goal of the study we present in this paper. We calculate
the yields of \Ni{56} in simulaitons of thermonuclear supernovae. Because
the radioactive decay of \Ni{56} powers the light curve of an event, 
the yield of \Ni{56} serves as a proxy for the event and allows us to
discern trends in brightness. Our study thus can offer theoretical 
insight into what events might be explained by explosions from these
progenitors as well as the overall scatter in the brightness
of observed events.

Our simulational methododolgy is described in the next section and 
our results, a comparison of nucleosynthetic explosion yields between these
new mixed hybrid C-O-Ne progenitors and traditional C-O progenitors
in the section following the methodology. Our results show systematic
differences in the yield of \Ni{56} between explosions from the two
types of progenitors, which we quantify and disuss.
}

@@

The need for a model flame in simulating thermonuclear supernovae follows
from the scales of the problem. At high densities, the width of a laminar
nuclear flame is $< 1\ensuremath{\;}{\ensuremath{\mathrm{cm}}}$ while the
radius of the white dwarf $\sim 10^9\ensuremath{\;}{\ensuremath{\mathrm{cm}}}$.
Even with adaptive mesh refinement, whole-star simulations cannot
simultaneously resolve the nuclear flame, so simulations require a model to
describe the burning on unresolved scales.  The model we apply is a flame
capturing scheme and thermally-activated burning module to describe
thermonuclear burning during both the deflagration and detonation phases,
as well as routines to describe the evolution of the dynamic ash.
This description of the burning was developed during the course of research in
thermonuclear supernovae and has been presented in a series of
papers \citep[See][and references therein]{townetal2016,chandlery}. For completeness,
we briefly review the flame capturing scheme here.

@@

We frame the presentation of the results of the suites of simulations
principally in terms of the yield of \Ni{56}, the energy source of
the light curve of an event. \Ni{56} thus serves as a proxy
for the brightness of an explosion and comparison of the yields
is equivalent to comparing the brightness of events. The
yields were estimated from $Y_e$ and the NSE progress variable, by 
assuming the composition upon NSE freeze-out is \Ni{56} plus equal
parts \Fe{54} and \Ni{58} \citep{townetal2009,Meaketal09}.
This assumption allows the fraction of IGEs in the form of \Ni{56} to be 
estimated from the $Y_e$ tracked by the burning model. 
{\color{blue}
This process has been shown to provide estimated \Ni{56} yields consistent with
the results of detailed network and NSE calculations~\cite{caldertownsley2018}.
}

\begin{figure}
\includegraphics[width=\columnwidth]{figures/cum_dis_Ni56.pdf}
\caption{\label{fig:cumdist}
The cumulative distribution of the final \Ni{56} yield for explosions from
C-O (red) and hybrid C-O-Ne (blue) models.
The curve for the hybrid models is shifted
to the left, indicating that explosions from hybrid progenitors produce
less \Ni{56} than explosions from traditional C-O models with the same central density.
}
\end{figure}
The cumulative distribution of the \Ni{56} yield for explosions from
C-O and hybrid C-O-Ne models is presented in Figure \ref{fig:cumdist}.
Average and standard deviations of the sample of yields and kinetic energies are given in Table~\ref{tab:ave_yields}.
The figure shows that the hybrid models consistently have a higher
cumulative fraction at a given mass of \Ni{56}, which indicates
that the yields of \Ni{56} are consistently lower in explosions
from hybrid progenitors of the same central density.
This contrast is in a similar direction but not as large as the difference 
between C-O and C-O-Ne progenitors seen in \citet{willcoxetal2016}.

@@

The production of \Ni{56}, after NSE freeze-out, as a function of simulation time
for 10 simulations of explosions from each progenitor is shown in Figure \ref{fig:nithybrid}.
{\color{blue} The sharp increase in the yield occuring after approximately 1.0 second indicates
the transiton to the detonation phase with its significantly faster burning. The curves
indicate that on average, the C-O models reach the DDT sooner then the hybrid model.}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/RatioNi56IGE_v_time_plot.pdf}
\caption{\label{fig:compare_ratio}
Expected ratio of \Ni{56} to total IGE production by mass vs.\ time showing the evolution
for both suites of simulations. 
{\color{red} Shown are realizations 21-30.}
Results from C-O-Ne progenitors are in blue and C-O progenitors in red.
%SAME AS DON'S FIGURE 19
}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{figures/MBTI_v_time_plot.pdf}
\caption{\label{fig:compare_burned}
Plot of estimated mass burned to IGEs vs.\ time showing the evolution
for both suites of simulations for realizations 25-30. Results from C-O-Ne progenitors are
in blue and C-O progenitors red.
%SAME AS DON'S FIGURE 20
}
\end{figure}

{\color{blue} 
The evolution of the fraction, by mass, of IGE material expected to be in the form of \Ni{56} after 
freeze-out is shown in Figure \ref{fig:compare_ratio}. 
Also shown in 
%Figure~\ref{fig:compare_burned} 
is the concurrent evolution of mass burned to IGE for both suites.
The total IGE has a mostly similar evolution, but the ratio demonstrates important differences between C-O and C-O-Ne cases.
}
